Convex Surrogates via Polyhedral Losses

### 2019-05-03 neurips-19/poly-embed.tex
Filling in proofs, mod lots of details

  First, suppose $L$ embeds $\ell$.
  We want to show that for all $p \in \simplex$ that $\inf_u\in\reals^d L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Fix $p \in \simplex$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then 
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.

  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
  \jessie{Slightly stuck on the nuances at the moment.  Will come back to it.}
\end{proof}

@@

  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
  For each facet $F$ of $\risk{L}$, consider the report $u = \arginf_{u'} L(u', p)$ for some $p \in \inter F$.
  (Note that this $u$ will be unique regardless of the choice of $p\in \inter F$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u\}$ \jessie{notate} is finite.
  Now define the discrete loss $\ell(r,y) = L(r,y)$ for all $r \in \R$.

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\jessiet{What if $\Gamma_u = \Gamma_{u'}$?  Wouldn't we remove both copies of the level set as is?}
\raft{Great point.  I changed to $\subsetneq$.}
\raft{Note for later: should be able to show that the union of trim is the simplex.}

>>>>

  First, suppose $L$ embeds $\ell$.
  We want to show that for all $p \in \simplex$ that $\inf_u\in\reals^d L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Fix $p \in \simplex$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then 
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.

  \jessie{Slightly stuck here.  Will revisit, but just FYI.}
  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
  Let $F$ be the set of facets in $\risk{\ell}$.
  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.  My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.  Does that make sense?}

\end{proof}

@@

  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
  For each facet $f$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
  Now define the discrete loss $\ell(r,y) = L(r,y)$ for all $r \in \R$.

@@

\begin{definition}\label{def:trim}
  Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}
\raft{Note for later: should be able to show that the union of trim is the simplex.}
